We piece together the sub-problems into the complete algorithm.
We will assume that we remove unit clauses and pure literals at each appropriate step.


\subsection{2-SAT Solver}
\label{subsec:2-sat-solver}

Consider a 2-SAT instance, $\Phi$ of size $(m,~ n)$.
Partition $\Phi$ about some choice of variable, $x_j$, to obtain $\phi_{left}$ and $\phi_{right}$.
$\phi_{left}$ is a base-case instance, while $\phi_{right}$ is a smaller 2-SAT instance which we will solve recursively.

Note that if $\Phi$ is satisfiable, then $\phi_{left}$ and $\phi_{right}$ are also satisfiable and each has at least one certificate compatible with the other.

Now consider a base-case 2-SAT instance, $\phi$.
Partition $\phi$ into $\phi_1$ and $\phi_2$ such that $\phi_1$ has only those clauses that contain $x_j$ and $\phi_2$ has only those clauses that contain $\lnot x_j$.

There are at most two possible certificates for each of $\phi_1$ and $\phi_2$.
For $\phi_1$, let us call these certificates $\rchi_{1\alpha}$ and $\rchi_{1\beta}$.

$\rchi_{1\alpha}$ and $\rchi_{1\beta}$ are defined as follows:
\begin{align*}
    \rchi_{1\alpha} & \coloneqq \{ x_j \mapsto T \} \\
    \rchi_{1\beta} & \coloneqq \{ x_j \mapsto F,~ all~ other~ literals \mapsto T \}
\end{align*}

$\rchi_{1\beta}$ exists if and only if all variables, other than $x_j$, are present as pure literals, i.e.\ if a variable is present then its negation is absent.

By symmetry, we have:
\begin{align*}
    \rchi_{2\alpha} & \coloneqq \{ x_j \mapsto F \} \\
    \rchi_{2\beta} & \coloneqq \{ x_j \mapsto T,~ all~ other~ literals \mapsto T \}
\end{align*}

for $\phi_2$.
Note that $\rchi_{1\alpha} \subset \rchi_{2\beta}$ and $\rchi_{2\alpha} \subset \rchi_{1\beta}$.

If $\phi$ is satisfiable, then $\phi_1$ and $\phi_2$ are also satisfiable and each has at least one certificate compatible with the other.
$\rchi_{1\alpha}$ is not compatible with $\rchi_{2\alpha}$.
Therefore either one or both of the following must be true:
\begin{align*}
    \exists !~ & \rchi_{1\beta}~ compatible~ with~ \phi_2 \\
    \exists !~ & \rchi_{2\beta}~ compatible~ with~ \phi_1
\end{align*}

Therefore either one or both of $\rchi_{1\beta}$ and $\rchi_{2\beta}$ are certificates for $\phi$.

Following this procedure gives us all certificates for each pair of sibling instances.
We then discard those certificates that are not compatible with their sibling instance.
We then obtain the certificates for the parent instance by performing pairwise unions between the remaining certificates from each sibling.


\subsection{3-SAT Solver}
\label{subsec:3-sat-solver}

$\dots$
